Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
intro stuff

\newcommand{\Nfp}{5}
\newcommand{\Nvalidated}{18} 
\newcommand{\Nlimbo}{13} %adds up to 36

@@

There has been considerable effort to recover these planetary signals.
\citet{Vanderburg14} extract aperture photometry and de-correlate with image centroid
position to calibrate the photometry as a function of position.
These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
binary systems and to identify a transiting system near a 3:2 period commensurability
\citep{Armstrong15b}.
\citet{Aigrain15} use a Gaussian Process model for the measured
flux, with pointing measurements as the inputs, and then ``de-trend'' the data with that model.
\citet{Crossfield15} apply a very similar method, which was used to detect the first 
multi-planet system in \KT\ data.

What is common to all of these methods are that removal of systematics is considered a
step to be undertaken before the search for planets.
Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
while retaining all of the astrophysical signal.
Of course, it is impossible to perfectly separate the astrophysical and instrumental
signal, and such a technique is prone to either over-fitting, in which some of the
astrophysical signal is also removed, or under-fitting, in which some
of the instrumental systematics remain.
A better strategy is to simultaneously fit both the signal and the systematics, as is common
practice in cosmology and, increasingly, in radial velocity searches for planetary systems
\citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.

@@

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-based
seeing-limited survey data, and adaptive optics imaging, we are able to confirm
\Nvalidated\ of these systems as transiting planets at the 99\% confidence
level. 
Additionally, we identify four systems as false positives.

@@

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 21 candidates
have FPP $<$ 1\%.  
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.

>>>>

\newcommand{\Nfp}{6}
\newcommand{\Nvalidated}{18} 
\newcommand{\Nlimbo}{12} %adds up to 36

@@

There has been considerable effort to recover these planetary signals, and to date six
planets have been confirmed in the \KT\ data 
\citep{Vanderburg15, Crossfield15, Armstrong15b}.
What is common to all of these methods are that removal of systematics is considered a
step to be undertaken before the search for planets.
Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
while retaining all of the astrophysical signal.
Of course, it is impossible to perfectly separate the astrophysical and instrumental
signal, and such a technique is prone to either over-fitting, in which some of the
astrophysical signal is also removed, or under-fitting, in which some
of the instrumental systematics remain.
A better strategy is to simultaneously fit both the signal and the systematics, as is common
practice in cosmology and, increasingly, in radial velocity searches for planetary systems
\citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.

@@

In this paper, we present stellar and planetary parameters for each system.
We also analyze the false positive probability of each system using \texttt{vespa},
a new publicly available, general-purpose implementation 
of the \citet{Morton12} procedure
to calculate false positive probabilities (FPPs) for transiting planets.
Through this analysis, as well as archival imaging, ground-based
seeing-limited survey data, and adaptive optics imaging, we are able to confirm
\Nvalidated\ of these systems as transiting planets at the 99\% confidence
level. 
Additionally, we identify six systems as false positives.

@@

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 20 candidates
have FPP $<$ 1\%.  
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.
